Verifying Demonstrations

### 2019-02-27 paper/verifiability-analysis.tex
Minor edit in verifiability-analysis

Finally, in the case of trusted witnesses, Alice's chance of corrupting 
witnesses is reduced to the trustworthiness of the witnesses chosen by the 
verifier.
In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
succeeds only if she can corrupt at least \(\theta\) witnesses.

>>>>

Finally, Alice can corrupt witnesses.
In the case of trusted witnesses, Alice's chance of corrupting witnesses is 
reduced to the trustworthiness of the witnesses chosen by the verifier.
In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
succeeds only if she can corrupt at least \(\theta\) witnesses.
